Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-27 survey/survey.tex
first pass on all of 4.2 done.

The constructs in Fig.~\ref{figc} are significantly more subtle.
\jc{WAVEFRONT}

@@

The constructs in Fig.~\ref{figb} \ldots
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

@@

The constructs in Fig.~\ref{figa} \ldots
\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\end{tikzpicture}
\end{center}

>>>>

The constructs in Fig.~\ref{figc} are significantly more subtle, as they
deal with combinators involving $0$, aka an impossibility.  For example,
\[  {(c \otimes \idc_{0}) \odot \absorbl \Leftrightarrow \absorbl \odot \idc_{0}}
\]
(where we have explicitly annotated the types of $\idc$ for increased clarity)
tells us that of the two ways of transforming from $t_1 \times 0$ to $0$, 
namely first doing some arbitrary transformation $c$ from $t_1$ to $t_2$ and
(in parallel) leaving $0$ alone then eliminating $0$, or first eliminating $0$
then doing the identity (at $0$), are equivalent. This is the ``naturality'' of
$\absorbl$. One item to note is the fact that this combinator is not
irreducible, as the $\idc$ on the right can be eliminated. But that is actually
a property visible at an even higher level (which we will not touch in this
paper).  The next $3$ are similarly expressing the naturality of $\absorbr$,
$\factorzl$ and $\factorzr$.

The next combinator, $\absorbr \Leftrightarrow \absorbl$,
is particularly fascinating: while it says something simple ---
that the two obvious ways of transforming $0 \times 0$ into $0$, namely
absorbing either the left or right zero --- it implies something subtle.
A straightforward proof of $\absorbl$ which proceeds by saying that
$0 \times t$ cannot be inhabited because the first member of the pair
cannot, is not in fact equivalent to $\absorbr$ on $0 \times 0$.
However, if we instead define $\absorbl$ to ``transport'' the
putative impossible first member of the pair to its (equally
impossible) output, then these do form equivalent pairs.
The next few in Fig.~\ref{figc} also express how $\absorbr$ and
$\absorbl$ interact with other combinators. As seen previously,
all of these arise as critical pairs. What is much more subtle here
is that the types involved often are asymmetric: they do not have
the same occurences on the left and right. Such cases are
particularly troublesome for finding normal forms \jc{should add
some citations here}.

@@

@@

The constructs in Fig.~\ref{figb} and Fig.~\ref{figa} relating associativity and
distributivity, and commutativity and distributivity, have more in common with
previous sets of combinators.  They do arise from non-trivial critical pairs
of different ways of going between equivalent types. The last one of
Fig.~\ref{figb} is particularly daunting, involving a sequence of $3$ combinators
on the left and $6$ on the right.
